### 2018-11-10 VV556/HW7/submission.tex
add ex3&4

\section{Exercise7.2}

\section{Exercise7.3}

\section{Exercise7.4}

>>>>

\section{Exercise7.2}
	\begin{enumerate}
		\item

\section{Exercise7.3}
	\begin{enumerate}
		\item 
			\begin{proof}
				It's clear that $L^{-1}$ is the differentiate operator, and $L^{-1}$ is unbounded. So $L$ has unbounded inverse.\\
				Since the domain of $L$ is composed of square-integrable functions over $[0,1]$, say
				\begin{equation}
					\int_{0}^{1} f^2(x) dx < \infty
				\end{equation}
				An element within the range of $L$ is
				\begin{equation}
					g(x) = \int_{0}^{x} f(t) dt
				\end{equation}
				Then, if $f(x)$ is a polynomial in $L^2$ , it must be bounded over $[0, 1]$ as it is continous. Denote the supreme of $f(x)$ as $M$, then $g(x) \leq Mx$. Hence $g(x)$ is square-integrable over $[0,1]$, say
				\begin{equation}
					\int_{0}^{1} g^2(x) dx \leq M^2 \int_{0}^{1} x^2 dx < \infty
				\end{equation}
				Clearly, the domain of $L$ doesn't contain all the polynomials and therefore the range of $L$ is open and incomplete. The boundary of the range of $L$ are the limits of squences like $f_n(x) = nx$ when $n\rightarrow \infty$.\\
				Hence, the state of $L$ is $(III, 1_n)$.
			\end{proof}
		\item 
			\begin{equation}
				L^* = L
			\end{equation}

\section{Exercise7.4}
	\begin{proof}
		For $p = 1$
		\begin{equation}
			\begin{aligned}
				RHS & \triangleq ||(a_n)||_1 \cdot ||(b_n)||_1 = \sum_{i=0}^{\infty} |a_i| \cdot \sum_{j=0}^{\infty} |b_j| = \sum_{n=0}^{\infty} \sum_{i+j=n} |a_i||b_j|\\
				 & \geq \sum_{n=0}^{\infty} |\sum_{i+j=n} a_i b_j| = \sum_{n=0}^{\infty} |c_n| = ||(c_n)||_1 \triangleq LHS
			\end{aligned}
		\end{equation} 
		For $p>1$, take $q > 0$ s.t. $\frac{1}{p} + \frac{1}{q} = 1$\\
		Then, using the Holder's inequality
		\begin{equation}
			\begin{aligned}
				LHS & \triangleq ||(c_n)||_p = \Big(\sum_{n=0}^{\infty} |c_n|^p\Big)^{\frac{1}{p}} = \Big(\sum_{n=0}^{\infty} \Big|\sum_{i+j=n}a_i b_j\Big|^p\Big)^{\frac{1}{p}}\\
				& = \Big(\sum_{n=0}^{\infty} \Big|\sum_{i+j=n}a_i b_j^\frac{1}{p} b_j^{\frac{1}{q}}\Big|^p\Big)^{\frac{1}{p}} \leq  \Big(\sum_{n=0}^{\infty} \Big|\sum_{i+j=n}\Big(|a_i| |b_j|^\frac{1}{p}\Big) |b_j|^{\frac{1}{q}}\Big|^p\Big)^{\frac{1}{p}}\\
				& \leq \Big(\sum_{n=0}^{\infty} \Big[\Big(\sum_{i+j=n}|a_i|^p |b_j|\Big)^\frac{1}{p} \Big(\sum_{j=0}^{n}|b_j|\Big)^\frac{1}{q}\Big]^p\Big)^{\frac{1}{p}} \\ 
				& = \Bigg[\sum_{n=0}^{\infty} \Big(\sum_{i+j=n}|a_i|^p |b_j|\Big) \Big(\sum_{j=0}^{n}|b_j|\Big)^\frac{p}{q}\Bigg]^\frac{1}{p} \\
				& \leq \Big(\sum_{i=0}^{\infty}|a_i|^p\Big)^\frac{1}{p}\cdot\Big(\sum_{j=0}^{\infty}|b_j|\Big)^\frac{1}{p}\cdot\Big(\sum_{j=0}^{\infty}|b_j|\Big)^\frac{1}{q}\\
				& = ||(a_n)||_p \cdot ||(b_n)||_1 \triangleq RHS
			\end{aligned}
		\end{equation}
	\end{proof}
